\documentclass[11pt]{article}

\usepackage{url}

%%  Dimensions
%%
\topmargin             0in
\headheight            0in
\headsep               0in
\textheight          8.5in
\textwidth           6.5in
\evensidemargin        0in
\oddsidemargin         0in

%%  Definitions
%%
\renewcommand{\baselinestretch}{1.1}
\pagestyle{plain}

\begin{document}

\begin{center}
{\bfseries \LARGE Task 4 -- Data Management\\[8mm]}
\end{center}


\section{SQLite}

SQLite is an in-process library that implements a self-contained, serverless, zero-configuration, transactional SQL database engine.
It is ACID-compliant and implements most of the SQL standard.
SQLite is a popular choice as embedded database for local/client storage in application software, and it has bindings to many programming languages.
Pertinent information about SQLite can be found on the project website.
\begin{itemize}
\item \url{http://www.sqlite.org/}
\end{itemize}


\subsection*{Action Items}

\begin{itemize}
\item \textbf{Read:} About SQLite. \\
\url{http://www.sqlite.org/about.html}
\item \textbf{Read:} Getting Started. \\
\url{http://www.sqlite.org/quickstart.html}
\item \textbf{Download and Install:} SQLite (if needed). \\
\url{http://www.sqlite.org/download.html}
\end{itemize}


\section{Database Browser for SQLite (optional)}

Database Browser for SQLite is a visual tool to create, design, and edit database files compatible with SQLite.
It is employed by users and developers who want to create databases, search, and edit data.
\begin{itemize}
\item \url{http://sqlitebrowser.org/}
\end{itemize}

\subsection*{Action Items}

\begin{itemize}
\item \textbf{Download and Install:} Database Browser for SQLite. \\
\url{http://www.sqlite.org/download.html}
\end{itemize}

\end{document}

