\documentclass[11pt]{article}

\usepackage{url}

%%  Dimensions
%%
\topmargin             0in
\headheight            0in
\headsep               0in
\textheight          8.5in
\textwidth           6.5in
\evensidemargin        0in
\oddsidemargin         0in

%%  Definitions
%%
\renewcommand{\baselinestretch}{1.1}
\pagestyle{plain}


\begin{document}

\begin{center}
{\bfseries \LARGE Task 5 -- Data Visualization\\[8mm]}
\end{center}


\section{Qt Project}

Qt is a cross-platform application and user interface (UI) framework for developers using C++ or QML.
Qt Creator is the supporting Qt IDE.
Qt and related tools are developed as an open source project.

\begin{center}
\url{http://qt-project.org/}
\end{center}


\section*{Action Items}

\begin{itemize}
\item \textbf{Read:} Getting Started with Qt. \\
\url{http://qt-project.org/doc/qt-5/gettingstarted.html}
\item \textbf{Peruse:} Qt Developer Guides. \\
\url{http://qt-project.org/wiki/developer-guides}
\item \textbf{Download and Install:} QT SDK and Qt Creator IDE. \\
\url{http://qt-project.org/downloads}
\item \textbf{Complete and Build:} Basic Tutorial. \\
\url{http://qt-project.org/wiki/Basic_Qt_Programming_Tutorial}
\end{itemize}


\section{QCustomPlot}

QCustomPlot is a Qt C++ widget for plotting and data visualization.
This plotting library focuses on making good looking, publication quality 2D plots, graphs and charts, as well as creating real-time visualization applications.
 
\begin{center}
\url{http://www.qcustomplot.com/}
\end{center}


\section*{Action Items}

\begin{itemize}
\item \textbf{Read:} Setting up QCustomPlot. \\
\url{http://www.qcustomplot.com/index.php/tutorials/settingup}
\item \textbf{Complete and Build:} Basics of Plotting. \\
\url{http://www.qcustomplot.com/index.php/tutorials/basicplotting}
\end{itemize}


\end{document}

